---
title: "XARINGAN"
subtitle: "Slideshows written with R Markdown"
author: "Michael DeCrescenzo"
date: "September 19, 2018"
output:
  xaringan::moon_reader:
    lib_dir: libs
    mathjax: "https://cdn.bootcss.com/mathjax/2.7.1/MathJax.js?config=TeX-AMS_HTML"
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

class: center, inverse, middle

## This slideshow was created using R Markdown


```{r setup, include = FALSE, cache = TRUE, echo = FALSE}
# chunks options:
# hide code and messages by default (warning, message)
# cache everything 
knitr::opts_chunk$set(eval = TRUE, 
                      warning = FALSE, message = FALSE,
                      cache = TRUE,
                      fig.retina = 2,
                      fig.align = "center", dpi = 100)

# Xaringan settings
library("xaringan")
library("xaringanthemer")

mono_light(base_color = "#002b36",
          link_color = "#2aa198",
          header_font_google = google_font("Vollkorn"), 
          text_font_google = google_font("PT Sans"), 
          code_font_google = google_font("Inconsolata"), 
          code_inline_background_color    = "#F5F5F5", 
          table_row_even_background_color = "white", 
          extra_css = 
            list(".remark-slide-number" = list("display" = "none"), 
                 ".remark-inline-code" = list("background" = "#F5F5F5", 
                                                #e7e8e2; /* darker */
                                              "border-radius" = "3px", 
                                              "padding" = "4px")))
```


---


## The gist

--

Slide breaks with `---`

--

Incremental slides with `--`

--

Text can be _styled_ using **Markdown**

--

$\mathrm{\LaTeX}$ math: $y_i = \alpha + x_i \beta$ 

--

Include R code and output:

```{r}
die <- 1:6
sample(die, 2, replace = TRUE)
```





---

class: center, middle, inverse

## Xaringan

### Beamer killer (?)



---

class: middle, center


### Install from Github

```{r, eval = FALSE}
devtools::install_github("yihui/xaringan")
```

### Read the documentation

<https://slides.yihui.name/xaringan/>


### Write an `.rmd` file

Output format `xaringan::moon_reader`

Easy customization using `xaringanthemer` R package


---

class: inverse, middle, center

# How it works

#### (It's kind of a hack)


---

class: middle, center

1. `.rmd` file is compiled to `.html`

2. Open file in web browser

2. Page is styled by the `remark.js` library (online)

1. Math is rendered by `MathJax`


---

class: center, middle, inverse

# Isn't this great? 

Control control (just like $\mathrm{\LaTeX}$)

Nicer code (open the source file)

Pretty slides



---

class: center, middle

## Learn more online

The online documentation (a Xarginan slideshow itself) is great

Check out `xaringanthemer` package



---

class: center, middle, inverse

### fin



